### 2020-01-18 all_models.tex
fixed GPT2 plots

\charlesx{We actually don't run regressions on all these datasetsm, BUT we could present them in the Figure below to show that alpha is a good metric for these kinds of models, in contrast to the NLP, where alpha is frequently too large to run a regression}

>>>>

\charles{We actually don't run regressions on all these datasetsm, BUT we could present them in the Figure below to show that alpha is a good metric for these kinds of models, in contrast to the NLP, where alpha is frequently too large to run a regression}

### 2020-01-18 nlp_models.tex
fixed something that couldn't compile
added serenas text
fixed GPT2 plots

\begin{table}[t]
\small
\begin{center}
\begin{tabular}{|p{1in}|c|c|c|c|c|}
\hline
   &    & Frobenius Norm & Spectral Norm & Weighted Alpha & Alpha-Norm \\
 Series & \#Layers   & $\Vert\mathbf{W}\Vert_{F}$ & $\Vert\mathbf{W}\Vert_{\infty}$ & $\hat{\alpha}=\alpha\log\lambda_{max}$ & $\Vert\mathbf{X}\Vert^{\alpha}_{\alpha}$ \\
\hline
 GPT & & & & &\\
GPT2 & 50 & 2.05 &2.59& 9.78 & 10.03 \\
GPT2 medium & 98 & 2.08 &2.58& 9.74 & 10.01 \\
GPT2 large & 146 & 1.85 &1.99& 7.67 & 7.94 \\
GPT2 xl & 194 & 1.86 &1.92& 7.17 & 7.51 \\

@@

\hline
\end{tabular}
\end{center}
\caption{Average Log Norm Metrics for pretrainnd OpenAI GPT and GPT2 models.}
\label{table:nlp}
\end{table}

@@

@@

    \subfigure[ Power Law Exponent $\alpha$  ]{
        \includegraphics[width=4.5cm]{img/GPT2_fnl_alpha_hist.png}
        \label{fig:gpt-alpha-layer}
    }
    \qquad
    \subfigure[ Spectral Norm $\Vert\mathbf{W}\Vert_{\infty}$]{
        \includegraphics[width=4.5cm]{img/GPT2_fnl_spectralnorm_hist.png}
        \label{fig:resnet-snorm-layer}
    }
    \qquad
    \subfigure[ Alpha-Norm $\Vert\mathbf{X}\Vert_{\alpha}^{\alpha}$]{
        \includegraphics[width=4.5cm]{img/GPT2_fnl_alpha_weighted_hist.png}
        \label{fig:gpt-pnorm-layer}
    }
    \caption{Comparison of Power Law Exponnents, Spectral Norm, and Alpha-Norm for different size models in the GPT2 architecture series.    }
    \label{fig:gpt-alpha-layers}
\end{figure}

>>>>

\begin{table}[t]
\small
\begin{center}
\begin{tabular}{|p{1in}|c|c|c|c|c|}
\hline
   &    & Frobenius Norm & Spectral Norm & Weighted Alpha & Alpha-Norm \\
 Series & \#Layers   & $\Vert\mathbf{W}\Vert_{F}$ & $\Vert\mathbf{W}\Vert_{\infty}$ & $\hat{\alpha}=\alpha\log\lambda_{max}$ & $\Vert\mathbf{X}\Vert^{\alpha}_{\alpha}$ \\
\hline
 GPT & & & & &\\
GPT2 & 50 & 2.05 &2.59& 9.78 & 10.03 \\
GPT2 medium & 98 & 2.08 &2.58& 9.74 & 10.01 \\
GPT2 large & 146 & 1.85 &1.99& 7.67 & 7.94 \\
GPT2 xl & 194 & 1.86 &1.92& 7.17 & 7.51 \\
\hline
\end{tabular}
\end{center}
\caption{Average Log Norm Metrics for pretrainnd OpenAI GPT and GPT2 models.}
\label{table:nlp}
\end{table}

@@

@@

\charles{We have redo the spectral norm and remove the outliers}

@@

    \subfigure[ Power Law Exponent $\alpha$  ]{
        \includegraphics[width=4.5cm]{img/GPT2_all_alpha_hist.png}
        \label{fig:gpt-alpha-layer}
    }
    \qquad
    \subfigure[ Spectral Norm $\Vert\mathbf{W}\Vert_{\infty}$]{
        \includegraphics[width=4.5cm]{img/GPT2_all_spectralnorm_hist.png}
        \label{fig:resnet-snorm-layer}
    }
    \qquad
    \subfigure[ Alpha-Norm $\Vert\mathbf{X}\Vert_{\alpha}^{\alpha}$]{
        \includegraphics[width=4.5cm]{img/GPT2_all_alpha_weighted_hist.png}
        \label{fig:gpt-pnorm-layer}
    }
    \caption{Comparison of Power Law Exponnents, Spectral Norm, and Alpha-Norm for different size models in the GPT2 architecture series.    }
    \label{fig:gpt-alpha-layers}
\end{figure}
